### 2016-02-04 mcmc.tex
refs

\clearpage
\raggedright
\begin{thebibliography}{}\markright{References}
\bibitem[Box \& Draper(1987)]{box}
  Box,~G.~E.~P. \& Draper,~N.~R.\ 1987,
  \textit{Empirical Model Building and Response Surfaces},
  John Wiley \& Sons, New York, NY
  \isbn{978-0471810339}.
\bibitem[Brooks \etal(2011)]{mcmchandbook}
  Brooks,~S., Gelman~A., Jones~G., \& Meng,~X.-L., eds.\ 2011,
  \href{http://www.mcmchandbook.net/HandbookTableofContents.html}{\textit{Handbook of Markov Chain Monte Carlo}},
  Chapman and Hall~/~CRC Press
  \isbn{978-1-4200-7941-8}.
\bibitem[Foreman-Mackey \etal(2012)]{emcee}
  Foreman-Mackey,~D., Hogg,~D.~W., Lang,~D., \& Goodman,~J.\ 2012,
  \project{emcee}: The MCMC Hammer,
  \textit{Pubs.\,Astron.\,Soc.\,Pac.}\ \textbf{125} 306--312
  \doi{10.1086/670067}
  (also \arxiv{1202.3665}).
\bibitem[Gelman \etal(1996)]{gelman234}
  Gelman,~A., Roberts,~G.~O., \& Gilks,~W.~R., 1996,
  Efficient Metropolis jumping rules,
  \textit{Bayesian Stat.}\ \textbf{5} 599--607.
\bibitem[Geyer(2011)]{geyer}
  Geyer,~C.~J., 2011,
  \href{http://www.mcmchandbook.net/HandbookChapter1.pdf}{Introduction to Markov Chain Monte Carlo},
  in \citet{mcmchandbook}.
\bibitem[Hogg \etal(2010)]{fittingaline}
  Hogg,~D.~W., Bovy,~J., \& Lang,~D., 2010,
  Data analysis recipes: Fitting a model to data,
  \arxiv{1008.4686v1}.
\bibitem[Hou \etal(2014)]{fengji}
  Hou,~F., Goodman,~J., \& Hogg,~D.~W., 2014,
  The probabilities of orbital-companion models for stellar radial velocity data,
  \arxiv{1401.6128}.
\bibitem[Metropolis \etal(1953)]{metropolis}
  Metropolis,~N., Rosenbluth,~A.~W., Rosenbluth,~M.~N., Teller,~A.~H., \& Teller,~E., 1953,
  Equation of state calculations by fast computing machines,
  \textit{J.\ Chem.\ Phys.}, \textbf{21} 1087--1092.
\bibitem[Neal \etal(2011)]{hamiltonian}
  Neal,~R.~M., 2011,
  \href{http://www.mcmchandbook.net/HandbookChapter5.pdf}{MCMC Using Hamiltonian Dynamics},
  in \citet{mcmchandbook}.
\bibitem[van~der~Walt \etal(2011)]{numpy}
  van~der~Walt,~S., Colbert,~S.~C., \& Varoquaux,~G., 2011,
  The NumPy Array: A structure for efficient numerical computation,
  \textit{Computing in Sci.\ \& Eng.}\ \textbf{13}, 22--30
  \doi{10.1109/MCSE.2011.37}.
\end{thebibliography}

>>>>

\clearpage
\raggedright
\begin{thebibliography}{}\markright{References}
\bibitem[Box \& Draper(1987)]{box}
  Box,~G.~E.~P. \& Draper,~N.~R.\ 1987,
  \textit{Empirical Model Building and Response Surfaces},
  John Wiley \& Sons, New York, NY
  \isbn{978-0471810339}.
\bibitem[Brooks \etal(2011)]{mcmchandbook}
  Brooks,~S., Gelman~A., Jones~G., \& Meng,~X.-L., eds.\ 2011,
  \href{http://www.mcmchandbook.net/HandbookTableofContents.html}{\textit{Handbook of Markov Chain Monte Carlo}},
  Chapman and Hall~/~CRC Press
  \isbn{978-1-4200-7941-8}.
\bibitem[Foreman-Mackey \etal(2012)]{emcee}
  Foreman-Mackey,~D., Hogg,~D.~W., Lang,~D., \& Goodman,~J.\ 2012,
  \project{emcee}: The MCMC Hammer,
  \textit{Pubs.\,Astron.\,Soc.\,Pac.}\ \textbf{125} 306--312
  \doi{10.1086/670067}
  (also \arxiv{1202.3665}).
\bibitem[Gelman \etal(1996)]{gelman234}
  Gelman,~A., Roberts,~G.~O., \& Gilks,~W.~R., 1996,
  \href{http://www.stat.columbia.edu/~gelman/research/published/baystat5.pdf}{Efficient Metropolis jumping rules},
  in Bernardo,~J.~M, Berger,~J.~O., Dawid,~A.~P., \& Smith,~A.~F.~M, eds.,
  \textit{Bayesian Statistics} \textbf{5}, Oxford University Press
  599--607.
\bibitem[Geyer(2011)]{geyer}
  Geyer,~C.~J., 2011,
  \href{http://www.mcmchandbook.net/HandbookChapter1.pdf}{Introduction to Markov Chain Monte Carlo},
  in \citet{mcmchandbook}, 3--48.
\bibitem[Hogg \etal(2010)]{fittingaline}
  Hogg,~D.~W., Bovy,~J., \& Lang,~D., 2010,
  Data analysis recipes: Fitting a model to data,
  \arxiv{1008.4686v1}.
\bibitem[Hou \etal(2014)]{fengji}
  Hou,~F., Goodman,~J., \& Hogg,~D.~W., 2014,
  The probabilities of orbital-companion models for stellar radial velocity data,
  \arxiv{1401.6128}.
\bibitem[Metropolis \etal(1953)]{metropolis}
  Metropolis,~N., Rosenbluth,~A.~W., Rosenbluth,~M.~N., Teller,~A.~H., \& Teller,~E., 1953,
  Equation of state calculations by fast computing machines,
  \textit{J.\ Chem.\ Phys.}, \textbf{21} 1087--1092.
\bibitem[Neal \etal(2011)]{hamiltonian}
  Neal,~R.~M., 2011,
  \href{http://www.mcmchandbook.net/HandbookChapter5.pdf}{MCMC Using Hamiltonian Dynamics},
  in \citet{mcmchandbook}, 113--162.
\bibitem[van~der~Walt \etal(2011)]{numpy}
  van~der~Walt,~S., Colbert,~S.~C., \& Varoquaux,~G., 2011,
  The NumPy Array: A structure for efficient numerical computation,
  \textit{Computing in Sci.\ \& Eng.}\ \textbf{13}, 22--30
  \doi{10.1109/MCSE.2011.37}.
\end{thebibliography}
